Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2019-03-08 article.tex
First incomplete draft of Methods, some fictional results, etc

% Affiliations
\usepackage{authblk}
\title{
  Transmembrane helices are also 
  an overlooked source of major histocompatibility complex class II epitopes
  and evolutionary more conserved than expected by change
}
\author[1]{Rich\`el J.C. Bilderbeek}
\author[1]{?Rampal S. Etienne}
\author[2]{Frans Bianchi}
\affil[1]{Groningen Institute for Evolutionary Life Sciences, University of Groningen, Groningen, The Netherlands}
\affil[2]{Frans' Institute, University of Groningen, Groningen, The Netherlands}

@@

The \verb;epitopeome; R package \cite{epitopeome} binds together 
the \verb;tmhmm; [\cite{tmhmm}] and \verb;netmhc2pan; [\cite{netmhc2pan}] 
R packages. \verb;tmhmm; provides an R interface to
TMHMM [\cite{krogh2001predicting}, \cite{sonnhammer1998hidden}], a tool
to predict where membrane proteins' amino acids are located within the
membrance.   
\verb;netmhc2pan; provides an R interface to
NetMHC2pan [\cite{jensen2018improved}], a tool
to predict MHC-II binding to proteins.

@@

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Appendix section 1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

% Affiliations
\usepackage{authblk}
\title{
  Transmembrane helices are also 
  an overlooked source of major histocompatibility complex class II epitopes
  and evolutionary more conserved than expected by chance
}
\author[1]{Rich\`el J.C. Bilderbeek}
\author[1]{?Rampal S. Etienne}
\author[2]{Frans Bianchi}
\affil[1]{Groningen Institute for Evolutionary Life Sciences, University of Groningen, Groningen, The Netherlands}
\affil[2]{Frans' Institute, University of Groningen, Groningen, The Netherlands}

@@

The \verb;epitopeome; R package \cite{epitopeome} binds \richel{pun intended} 
together the \verb;tmhmm; [\cite{tmhmm}] and \verb;netmhc2pan; [\cite{netmhc2pan}] 
R packages. \verb;tmhmm; provides an R interface to
TMHMM [\cite{krogh2001predicting}, \cite{sonnhammer1998hidden}], a tool
to predict where membrane proteins' amino acids are located within the
membrance.   
\verb;netmhc2pan; provides an R interface to
NetMHC2pan [\cite{jensen2018improved}], a tool
to predict MHC-II binding to proteins.

The evolutionary conservation of TMHs was measured from a
DNA alignment of multiple transmembrane proteins in multitiple
species of the mycoplasma bacterial family
\richel{how obtained exactly? how alignment done?}.

Using the \verb;tmhprot; R package [\cite{tmhprot}], the DNA alignment is split
into two alignments, one for the TMH parts, another for the non-TMH
parts. Each alignment was tested by the \verb;mcbette; 
R package [\cite{mcbette}] to select the Bayesian inference model with
the highest evidence (a.k.a. the marginal likelihood) using the nested
sampling approach as described in \cite{maturana2018model},
using the popular Bayesian phylogenetic tool 
BEAST2 [\cite{bouckaert2014beast}] in the back-end.
\verb;mcbette; used a set of 40 candidate inference models, 
consisting of all combinations of 
4 site models (JC, HKY, TN, GTR), 
2 clock models (strict, RLN) and 
5 tree priors (Yule, BD, CBS, CCP, CEP).

For each alignment, the inference model with the highest evidence
is used in a Bayesian inference. From each Bayesian posterior,
the parameter estimates regarding mutation rates (including clock rate)
were obtained and compared to determine which realized mutation rate is lower.
The Markov chain Monte Carlo was set up in such a way that the effective sample
size for the likelihood of the inference model is above the recommended value
of 200 [\cite{bouckaert2014beast}].

@@

Table \ref{tab:results} shows the location and binding strength for the
tuberculosis proteome.

@@

The inference model with the highest evidence in the
TMH-only alignment was [yet unknown] and [also yet unknown]
for the non-TMH alignment. Individual model weights are shown
in tables \ref{tab:evidences_tmh} 
and \ref{tab:evidences_non_tmh}.

The Bayesian inference resulted in [a distribution of mutation rates],
as shown in [absent figure].
The ESSes of the Bayesian parameter estimates was above 200, exact values
are shown in tables \ref{tab:esses_tmh} and \ref{tab:esses_non_tmh}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Model selection}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}[ht]
\centering
\begin{tabular}{rlllrr}
  \hline
 & Site model & Clock model & Tree prior & log(evidence) & Weight \\ 
  \hline
1 & JC & Strict & Yule & -8201.109 & 0.002 \\ 
  2 & JC & Strict & BD & -8203.346 & 0.000 \\ 
  3 & JC & Strict & CCP & -8195.927 & 0.278 \\ 
  4 & JC & Strict & CEP & -8194.976 & 0.720 \\ 
   \hline
\end{tabular}
\caption{
  Evidences for the TMH-only alignment
  \richel{These are just example values}
} 
\label{tab:evidences_tmh}
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{rlllrr}
  \hline
 & Site model & Clock model & Tree prior & log(evidence) & Weight \\ 
  \hline
1 & JC & Strict & Yule & -8201.109 & 0.002 \\ 
  2 & JC & Strict & BD & -8203.346 & 0.000 \\ 
  3 & JC & Strict & CCP & -8195.927 & 0.278 \\ 
  4 & JC & Strict & CEP & -8194.976 & 0.720 \\ 
   \hline
\end{tabular}
\caption{
  Evidences for the non-TMH alignment
  \richel{These are just example values}
} 
\label{tab:evidences_non_tmh}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Inference strength}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrr}
  \hline
 & posterior & likelihood & prior & treeLikelihood & TreeHeight & YuleModel & birthRate \\ 
  \hline
1 & 10001 & 10001 & 10001 & 10001 & 9913 & 10001 & 9540 \\ 
   \hline
\end{tabular}
\caption{
  ESSes of the TMH-only alignment
  \richel{These are just example values}
} 
\label{tab:esses_tmh}
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrr}
  \hline
 & posterior & likelihood & prior & treeLikelihood & TreeHeight & YuleModel & birthRate \\ 
  \hline
1 & 10001 & 10001 & 10001 & 10001 & 9913 & 10001 & 9540 \\ 
   \hline
\end{tabular}
\caption{
  ESSes of the non-TMH alignment
  \richel{These are just example values}
} 
\label{tab:esses_non_tmh}
\end{table}
